Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-02-07 paper/main.tex
Updates

To model how our learning procedure interacts with the data, we
assume that we have access to a second oracle $\mathcal{D}_G$ than can answer
d-separation queries with respect to the unknown target graph: 
$\mathcal{D}_G(X,Y,\mathbf{Z})=1$ iff $X \ci_G Y \mid \mathbf{Z}$. 
These are the standard oracles considered in constraint-based structure learning algorithms,
such as the PC algorithm \cite{Kalisch2012}. Based on this oracle, we now define two procedures
that iteratively change a current DAG structure.

@@

\begin{algorithm}[h]
\DontPrintSemicolon
\SetAlgoLined
\SetKwFunction{Expand}{Expand}
\SetKw{KwGoTo}{go to}
\SetKwProg{Fn}{Function}{:}{}
\Fn{{\sc Expand}($V,E,\mathcal{D}_G,\mathcal{A}_G$,$B=\emptyset$,$k=\infty$)}{
    let $L \gets \{\}$\;
    \ForEach{$X, Y$ where $X \to Y \notin E$ and $Y \to X \notin E$ and 
	$\{X,Y\} \notin B$}{
        let $\mathbf{Z}$ be a set that $d$-separates $X$ and $Y$ in $(V,E)$\;
        \If{$\mathcal{D}_G(X, Y, \mathbf{Z}) = 0$}{
            $L \gets L \cup \mathcal{A}_G(X, Y)$ \;
        }
	\If{$|L|\geq k$}{\KwGoTo 12\;}
    }
    add all edges in $L$ to $E$\;
    \Return{$(V,E)$}\;
}
\caption{Adding edges based on data an domain knowledge}
\label{algo:expand}
\end{algorithm}

>>>>

To model how our learning procedure interacts with the data, we assume that we
have access to a second oracle $\mathcal{D}_G$ than can answer d-separation
queries with respect to the unknown target graph:
$\mathcal{D}_G(X,Y,\mathbf{Z})=1$ iff $X \ci_G Y \mid \mathbf{Z}$. These are
the standard oracles considered in constraint-based structure learning
algorithms, such as the PC algorithm \cite{Spirtes2001}. Based on this oracle,
we now define two procedures that iteratively change a current DAG structure.

@@

\begin{algorithm}[h]
\DontPrintSemicolon
\SetAlgoLined
\SetKwFunction{Expand}{Expand}
\SetKw{KwGoTo}{go to}
\SetKwProg{Fn}{Function}{:}{}
\Fn{{\sc Expand}($V,E,\mathcal{D}_G,\mathcal{A}_G$,$B=\emptyset$,$k=\infty$)}{
    let $L \gets \{\}$\;
    \ForEach{$X, Y$ where $X \to Y \notin E$ and $Y \to X \notin E$ and 
	$\{X,Y\} \notin B$}{
        let $\mathbf{Z}$ be a set that $d$-separates $X$ and $Y$ in $(V,E)$\;
        \If{$\mathcal{D}_G(X, Y, \mathbf{Z}) = 0$}{
            $L \gets L \cup \mathcal{A}_G(X, Y)$ \;
        }
	\If{$|L|\geq k$}{\KwGoTo 12\;}
    }
    add all edges in $L$ to $E$\;
    \Return{$(V,E)$}\;
}
\caption{Adding edges based on data and domain knowledge}
\label{algo:expand}
\end{algorithm}
